---
title: "Survey_Data_Visualization"
author: "Lillian Horin (for Jarek Azim)"
output: 
  html_document:
    self-contained: false
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This code will visualize the data from the survey conducted by Jarek Azim. One thing to note here is that the survey was conducted on QuestionPro, whose export function is not friendly for R analysis. This makes digging deeper in the analysis difficult (e.g. seeing whether results stratified by nationality). QuestionPro better exported just the final data, but since that is very easy to just manually type here, that is what I will be doing.

# Data Import

First, loading in the libraries for organization and data visualization.

```{r Import-libraries, echo=T, message=FALSE, warning=FALSE}
# Load libraries
library(tidyverse)
library(RColorBrewer)
```

These next codes will be loading in the survey data. 

```{r Social-Impact}
# Create dataset
social_impact_data <- tibble(  
	Answer = c("Yes", 
	           "No", 
	           "Probably", 
	           "I've Never Noticed"), 
	Proportion = c(0.4932, 
	               0.0685, 
	               0.3699, 
	               0.0685)
)

social_impact_data


```

```{r Backlash}
# Create dataset
backlash_data <- tibble(Type = c("Historical Depictions", 
                                 "Historical Depictions", 
                                 "Historical Depictions", 
                                 "Historical Depictions", 
                                 "Historical Depictions", 
                                 "Political Insensitivity",
                                 "Political Insensitivity",
                                 "Political Insensitivity",
                                 "Political Insensitivity",
                                 "Political Insensitivity",
                                 "International Satire",
                                 "International Satire",
                                 "International Satire",
                                 "International Satire",
                                 "International Satire",
                                 "Discrimination",
                                 "Discrimination",
                                 "Discrimination",
                                 "Discrimination",
                                 "Discrimination",
                                 "Other",
                                 "Other",
                                 "Other",
                                 "Other",
                                 "Other"),
                        Answer = c("Often", 
                                   "Somewhat Often", 
                                   "Neutral", 
                                   "Somewhat Rare", 
                                   "Rare",
                                   "Often", 
                                   "Somewhat Often", 
                                   "Neutral", 
                                   "Somewhat Rare", 
                                   "Rare",
                                   "Often", 
                                   "Somewhat Often", 
                                   "Neutral", 
                                   "Somewhat Rare", 
                                   "Rare",
                                   "Often", 
                                   "Somewhat Often", 
                                   "Neutral", 
                                   "Somewhat Rare", 
                                   "Rare",
                                   "Often", 
                                   "Somewhat Often", 
                                   "Neutral", 
                                   "Somewhat Rare", 
                                   "Rare"),
                        Proportion = c(0.2958,
                                       0.4225,
                                       0.1268,
                                       0.1127,
                                       0.0423,
                                       0.4143,
                                       0.3857,
                                       0.1143,
                                       0.0571,
                                       0.0286,
                                       0.1449,
                                       0.2609,
                                       0.3913,
                                       0.1594,
                                       0.0435,
                                       0.4722,
                                       0.4167,
                                       0.056,
                                       0.056,
                                       0.00,
                                       0.1944,
                                       0.1389,
                                       0.6389,
                                       0.278,
                                       0.00)
)

backlash_data


```
```{r Groups-Engaging}
# Create dataset
groups_engaging_data <- tibble(Type = c("Individual Fans",
                                 "Individual Fans",
                                 "Individual Fans",
                                 "Individual Fans",
                                 "Individual Fans",
                                 "Fan Groups",
                                 "Fan Groups",
                                 "Fan Groups",
                                 "Fan Groups",
                                 "Fan Groups",
                                 "Media Representatives",
                                 "Media Representatives",
                                 "Media Representatives",
                                 "Media Representatives",
                                 "Media Representatives"),
                        Answer = c("Often", 
                                   "Somewhat Often", 
                                   "Neutral", 
                                   "Somewhat Rare", 
                                   "Rare",
                                   "Often", 
                                   "Somewhat Often", 
                                   "Neutral", 
                                   "Somewhat Rare", 
                                   "Rare",
                                   "Often", 
                                   "Somewhat Often", 
                                   "Neutral", 
                                   "Somewhat Rare", 
                                   "Rare"),
                        Proportion = c(0.2958,
                                       0.2958,
                                       0.2114,
                                       0.1127,
                                       0.0845,
                                       0.1014,
                                       0.3768,
                                       0.2319,
                                       0.2464,
                                       0.0435,
                                       0.0735,
                                       0.1765,
                                       0.2941,
                                       0.25,
                                       0.2059)
                        )
groups_engaging_data
```
```{r Political-SNS-Data}
# Create dataset
political_sns_data <- tibble(Type = c("Social Movement Organizations",
                                        "Social Movement Organizations",
                                        "Social Movement Organizations",
                                        "Social Movement Organizations",
                                        "Religious Movements",
                                        "Religious Movements",
                                        "Religious Movements",
                                        "Religious Movements",
                                        "Campaigning",
                                        "Campaigning",
                                        "Campaigning",
                                        "Campaigning",
                                        "Independent News Accounts",
                                        "Independent News Accounts",
                                        "Independent News Accounts",
                                        "Independent News Accounts",
                                        "Cultural Discourse",
                                        "Cultural Discourse",
                                        "Cultural Discourse",
                                        "Cultural Discourse",
                                        "Political Distrust, Emotions, or Support",
                                        "Political Distrust, Emotions, or Support",
                                        "Political Distrust, Emotions, or Support",
                                        "Political Distrust, Emotions, or Support"),
                               Answer = c("Never",
                                          "Sometimes",
                                          "Often",
                                          "Always",
                                          "Never",
                                          "Sometimes",
                                          "Often",
                                          "Always",
                                          "Never",
                                          "Sometimes",
                                          "Often",
                                          "Always",
                                          "Never",
                                          "Sometimes",
                                          "Often",
                                          "Always",
                                          "Never",
                                          "Sometimes",
                                          "Often",
                                          "Always",
                                          "Never",
                                          "Sometimes",
                                          "Often",
                                          "Always"),
                               Proportion = c(0.0149,
                                              0.2687,
                                              0.4627,
                                              0.2537,
                                              0.4773,
                                              0.3864,
                                              0.1136,
                                              0.0227,
                                              0.0781,
                                              0.4063,
                                              0.2969,
                                              0.2188,
                                              0.0667,
                                              0.5667,
                                              0.2667,
                                              0.10,
                                              0.00,
                                              0.2388,
                                              0.3582,
                                              0.4030,
                                              0.0149,
                                              0.2537,
                                              0.2985,
                                              0.4328)
)
political_sns_data
```


# Data Preparation

In order to visualize the graphs in a particular order, the data `levels` will be explicitly defined.

```{r Factor-levels, echo=T, message=F}
# Define order of answers that will be visualized
social_impact_data$Answer <- social_impact_data$Answer %>%
  factor(levels = c("Yes", "No", "Probably", "I've Never Noticed"))

backlash_data$Answer <- backlash_data$Answer %>%
  factor(levels = c("Often", "Somewhat Often", "Neutral", "Somewhat Rare", "Rare"))

backlash_data$Type <- backlash_data$Type %>%
  factor(levels = c("Historical Depictions", "Political Insensitivity", "International Satire", "Discrimination", "Other"))

groups_engaging_data$Answer <- groups_engaging_data$Answer %>%
  factor(levels = c("Often", "Somewhat Often", "Neutral", "Somewhat Rare", "Rare"))

groups_engaging_data$Type <- groups_engaging_data$Type %>%
  factor(levels = c("Individual Fans", "Fan Groups", "Media Representatives"))

political_sns_data$Answer <- political_sns_data$Answer %>%
  factor(levels = c("Always", "Often", "Sometimes","Never"))

political_sns_data$Type <- political_sns_data$Type %>%
  factor(levels = c("Social Movement Organizations", "Religious Movements", "Campaigning","Independent News Accounts","Cultural Discourse","Political Distrust, Emotions, or Support"))


# Check that all classes are factors

class(social_impact_data$Answer)
class(backlash_data$Answer)
class(backlash_data$Type)
class(groups_engaging_data$Answer)
class(groups_engaging_data$Type)
class(political_sns_data$Answer)
class(political_sns_data$Type)

```



# Visualize Data

Now time to visualize the data. For some reason, font changes aren't working here. 

```{r Social-Impact-Graph-Setup, warnings=FALSE}
# Social Media Impact Graph
social_impact_graph <- social_impact_data %>%
  ggplot(aes(x = Answer, y = Proportion, fill=Answer)) + 
  geom_bar(stat="identity", show.legend = FALSE) + 
  ggtitle('Do fan critics have an impact on political pressure, decisions, etc?') +
  ylab("% Respondents") + 
  scale_y_continuous(labels = scales::percent, limits=c(0,1))+
  geom_text(aes(label=scales::percent(Proportion), vjust=-0.3)) +
  theme(axis.title.x = element_blank(),
        plot.title = element_text(size=14))
```

```{r Social-Impact-Graph, fig.width = 10}
social_impact_graph
```


```{r Backlash-Graph, fig.width = 10}

backlash_graph <- backlash_data %>%
  ggplot(aes(x= Answer, Group=Type)) + 
  geom_bar(show.legend = FALSE, aes(y = Proportion, fill = factor(Type)), stat="identity") + 
  geom_text(aes( label = scales::percent(Proportion),y= Proportion ), stat= "identity", vjust = -.5, size = 3) +
  ggtitle('How often do TV shows, music, movies, etc receive backlash from its fan community for:') +
  labs(y = "% Respondents", fill="Type") +
  facet_grid(~Type) +
  scale_y_continuous(labels = scales::percent,limits=c(0,1)) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size=14))

backlash_graph
```
```{r Groups-Engaging-Graph, fig.width = 10}
# Groups Engaging Graph
groups_engaging_graph <-groups_engaging_data %>%
  ggplot(aes(x= Answer, Group=Type)) + 
  geom_bar(show.legend = FALSE, aes(y = Proportion, fill = factor(Type)), stat="identity") + 
  geom_text(aes( label = scales::percent(Proportion),y= Proportion ), stat= "identity", vjust = -.5, size = 3) +
  ggtitle('How often do you experience fans and fandoms engaging in such political activities?') +
  labs(y = "% Respondents", fill="Type") +
  facet_grid(~Type) +
  scale_y_continuous(labels = scales::percent,limits=c(0,1)) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size=14))

groups_engaging_graph

```
```{r Political-SNS-Graph, fig.width = 15}
political_sns_graph <- political_sns_data %>%
  ggplot(aes(x= Answer, Group=Type)) + 
  geom_bar(show.legend = FALSE, aes(y = Proportion, fill = factor(Type)), stat="identity") + 
  geom_text(aes( label = scales::percent(Proportion),y= Proportion ), stat= "identity", vjust = -.5, size = 3) +
  ggtitle('From your experience on social media, have you seen the following and to what extent?') +
  labs(y = "% Respondents", fill="Type") +
  facet_grid(~Type) +
  scale_y_continuous(labels = scales::percent,limits=c(0,1)) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size=14))
political_sns_graph
```


---
```{r Session-info}
sessionInfo()
```

